Out-of-Sample Comparisons of Overfit Models

### 2013-10-23 paper.tex
Remove references and theory for rolling and recursive windows
The rolling and recursive arguments in the paper are wrong---there is
an eigenvector that shows up when constructing the forecasts associated
with the estimators the blows up and prevents convergence.  This commit
removes that material from the paper.

Both models are estimated using \ols\ with a recursive, fixed, or
rolling window:
\[
\hat y_{i,t+\h} = x_{it}'\hat{\theta}_{it}^{R}, \qquad i=1,2, \qquad t
= R+1,\dots,T-h
\]
with
\begin{equation*}
  \bh{it}^{R} =  
  \begin{cases}\big(\sum_{s=1}^{t-\h} x_{is}x_{is}'\big)^{-1}
    \sum_{s=1}^{t-\h} x_{is} y_{s+\h} & \text{recursive window}\\
    \big(\sum_{s=t - \h - R}^{t-\h} x_{is}x_{is}'\big)^{-1}
    \sum_{s=t - \h - R}^{t-\h} x_{is} y_{s+\h} & \text{rolling window}\\
    \big(\sum_{s=1}^{R-\h} x_{is}x_{is}'\big)^{-1} \sum_{s=1}^{R-\h}
    x_{is} y_{s+\h} & \text{fixed window}
  \end{cases}
\end{equation*}
The observed \oos\ average is denoted $\oosA$: \[\oosA \equiv P^{-1}
\oosSum{t}{1} D_{Rt}\]  with
\[
D_{Rt} \equiv L(y_{t+\h} - x_{1t}'\bh{1t}^R) - L(y_{t+\h}
  - x_{2t}'\bh{2t}^R).
\]
The \oos\ statistic of interest is $\oost \equiv \sqrt{P} \oosA /
\hat\sigma_R$, for $\hat\sigma_R^2$ some (possibly Heteroskedasticity- and
Autocorrelation-Consistent, or \hac) estimator of the asymptotic
variance of $\oosA$.

As discussed above, the forecaster's goal is to choose the model with
lower average future loss; i.e. to determine whether $\oosB$ is
positive or negative,with
\[
\oosB \equiv Q^{-1} \sum_{t=T+1}^{T+Q} D_{Tt}, \quad 
D_{Tt} \equiv L(y_{t+h} - x_{1t}' \bh{1t}^T) - L(y_{t+h} - x_{2t}' \bh{2t}^T)
\]
and 
\begin{equation*}
  \bh{it}^{T} = 
  \begin{cases} \big(\sum_{s=1}^{t-\h} x_{is}x_{is}'\big)^{-1}
    \sum_{s=1}^{t-\h} x_{is} y_{s+\h} & \text{recursive window} \\
    \big(\sum_{s=t - \h - T}^{t-\h} x_{is}x_{is}'\big)^{-1}
    \sum_{s=t - \h - T}^{t-\h} x_{is} y_{s+\h} & \text{rolling window} \\
    \big(\sum_{s=1}^{T-\h} x_{is}x_{is}'\big)^{-1} 
    \sum_{s=1}^{T-\h} x_{is} y_{s+\h} & \text{fixed window}.
  \end{cases}
\end{equation*}
Note that the coefficients are reestimated with the full dataset.
Since the forecaster's information set, $\mathcal{F}_T$, does not
contain $\oosB$, he or she should decide between the models based on
the conditional expectation, $\E_T \oosB$. If this quantity is
positive, the first model is expected to perform the worst in the
future, and if it is negative the second is.

@@

\begin{asmp} \label{asmp-4} $P\to\infty$, $R\to\infty$, and  $P =
  o(T^{1/2}$) as $T \to \infty$.  For the rolling and recursive
  windows, $Q = o(T^{1/2})$ as well.
\end{asmp}

@@

Assumptions~\ref{asmp-1}--\ref{asmp-5} are broadly similar to
\citepos{Wes:96} assumptions, except with regard to model complexity
and the size of the test sample.  West assumes that $K_1$ and $K_2$
are both finite, while we let them grow rapidly with $T$
(Assumption~\ref{asmp-1}), and West lets $P/R$ converge to any value
in $[0,\infty]$, while we require $P^2/R \to 0$
(Assumption~\ref{asmp-4}).\footnote{\citet{Wes:96} does not have a
  second \oos\ period, so there is no analogue in his paper to our
  restriction on $Q$.}  Obviously, these differences are
related---allowing for complex models requires tighter constraints on
the size of the test sample.  West allows more general estimation
methods, while we restrict attention to \ols; the advantage of using
\ols\ is that we can derive the inequality, $$\| x_{it}'
\theta_{it}^{R} - x_{it}' \theta_{iR}^R \|_2 \leq O(P/T)^{1/2}.$$  Our
main results will hold for other models as long as a similar
inequality exists, but proving such inequalities for other models is
left for future research.

@@

Two intermediate Lemmas will help us understand Theorem
\ref{res-confidence-intervals} better.  Its proof consists of two
steps: we can write
\begin{equation}
  \sqrt{P} (\oosA - \E_T \oosB) = \sqrt{P} (\oosA - \E_R
  \oosA) + \sqrt{P} (\E_R \oosA - \E_T \oosB),
\end{equation}
so Theorem~\ref{res-confidence-intervals} holds if
\begin{equation}\label{coefpart}
  \E_R \oosA = \E_T \oosB + o_p(P^{-1/2}).
\end{equation}
and
\begin{equation}\label{normalpart}
  \sqrt{P}\frac{\oosA - \E_R \oosA}{\sigma_R} \to^d N(0,1)
\end{equation}
The first Lemma shows that the rolling and recursive window statistics
can be approximated by the fixed window statistic and that
that~\eqref{coefpart} holds for the fixed window.  The second Lemma
shows that the process $\{D_{Rt} - \E_R \oosA\}$ is an $L_2$-mixingale
of size $-1/2$ that satisfies a \clt\ for the fixed window statistic,
ensuring~\eqref{normalpart}.

\begin{lem} \label{res-convergence} Suppose that Assumptions
  \ref{asmp-1}--\ref{asmp-4} hold, let $D_{Rt}'$ and $D_{Tt}'$ denote
  the loss differences associated with the rolling or recursive
  window, and let $D_{Rt}$ and $D_{Tt}$ those of the fixed window.  Then
  \begin{equation}
    \label{eq:8}
    P^{1/2} (\oosA' - \oosA) \to^p 0, \qquad P^{1/2} (\oosB' - \oosB)
    \to^p 0,
  \end{equation}
  and
  \begin{equation}\label{eq:7}
    \E_T \oosB - \E_R \oosA =  O_p(\sqrt{P/T}) +
    o_p(P^{-1/2}).
  \end{equation}
\end{lem}

Note that $\E_T \oosB - \E_R \oosA$ is noise introduced by
approximating the performance of the full-sample estimates with that
of the partial-sample estimates.  Moreover, the $O_p(\sqrt{P/T})$ term
is binding; it is straightforward to find examples for which
$\sqrt{T/P}(\E_T \oosB - \E_R \oosA)$ does not converge to
zero.\footnote{Notice that, if the observations are i.i.d. and
  $(y_{t+h}, x_{it}) \sim N(0,I)$, $(\hat{\theta}_{iR}^R -
  \hat{\theta}_{iT}^T) \sim N(0, (X_{iR}'X_{iR})^{-1} -
  (X_{iT}'X_{iT})^{-1})$ given $X_{iT}$, and so
  $\var(x_{i,T+1}'\hat{\theta}_{iR}^R - x_{i,T+1}'
  \hat{\theta}_{iT}^T) \gg P K_i / (R - K_2)(T - K_2)$.}
Consequently, there is little scope to relax our assumption that
$P^2/T \to 0$.  If $\lim P^2/T$ is positive and finite then there is
the possibility of adjusting the asymptotic distribution of the test
statistic to account for this noise term as in \citet{Wes:96}, but we
leave that to future research.  If $P^2/T \to \infty$, which is
closest to common practice in applied research, the noise term
dominates the asymptotic distribution of the \oos\ $t$-test, so the
test has only trivial power in the limit if it has correct size.

@@

  \noindent Part 2: Moreover,~\eqref{normalpart} holds under the
  conditions of Part 1 if $P \to \infty$ as $T \to \infty$ and
  $\sigma_R^2$ is a.s. uniformly positive.
\end{lem}

@@

\begin{lem}
  \label{res-variance-estimator} Suppose Assumptions \ref{asmp-1},
  \ref{asmp-2}, \ref{asmp-3}, and \ref{asmp-5} hold, that $\gamma$,
  $P$, and $R \to \infty$ as $T \to \infty$, and that $\gamma = o(P)$
  and define
  \begin{equation*}
    \hat{\sigma}_R^2 \equiv P^{-1} \oosSum{s,t}{1} (D_{Rt} - \oosA)(D_{Rs} - \oosA)
    \vWeight.
  \end{equation*}
  Then $\hat{\sigma}_R^2 - \sigma_R^2 \to^p 0$.
\end{lem}

@@

Consider the fixed-window estimation scheme, let $L(e) = e^2$, let $h
= 1$, let the benchmark model have no regressors (i.e. $y_{t+1} \sim$
white noise), suppose that $(y_{t}, x_{2t}) \sim i.i.d.\ N(0,I)$, and
assume that $R > 2K_2 + 4$.\footnote{The restriction $R > 2 K_2 + 4$
  allows us to use a convenient formula for moments of the
  Inverse-Wishart distribution.}  Under these conditions,
\begin{align*}
  D_{Rt} &= 2 y_{t+1} x_{2t}'\hat{\theta}_{2R}^R -
  \hat{\theta}_{2R}^{R\prime} (x_{2t} x_{2t}') \hat{\theta}_{2R}^R \\
  D_{Tt} &= 2 y_{t+1} x_{2t}'\hat{\theta}_{2T}^T -
  \hat{\theta}_{2T}^{T\prime} (x_{2t} x_{2t}') \hat{\theta}_{2T}^T.
\end{align*}

The first two moments of $D_{Rt}$ for $t > R$ (conditional
on $\mathcal{F}_R$) are straightforward to derive:
$\E_R D_{Rt} = - \hat{\theta}_{2R}^{R\prime} \hat{\theta}_{2R}^R$
and
\begin{equation*}
  \sigma_R^2 \equiv \E_R(D_{Rt} - \E_R D_{Rt})^2 = 4
  \hat{\theta}_{2R}^{R\prime} \hat{\theta}_{2R}^{R} +
  \E_R(\hat{\theta}_{2R}^{R\prime} (I - x_{2t} x_{2t}')
  \hat{\theta}_{2R}^{R})^2   \geq 4 \hat{\theta}_{2R}^{R\prime}
  \hat{\theta}_{2R}^R \quad a.s.
\end{equation*}
Now, $\hat{\theta}_{2R}^{R\prime} \hat{\theta}_{2R}^R$ is
a.s. positive and uniformly integrable with mean $4 K_2 / (R - K_2 -
1)$ (since $(X_{2R}'X_{2R})^{-1}$ is Inverse-Wishart$(I_{K_2}, R)$),
making $\sigma_R^2$ uniformly a.s. positive and ensuring that the
distribution of the \oos\ average is not $P^{1/2}$-degenerate.  The
natural \oos\ variance estimator is consistent for $\sigma_R^2$:
\begin{align*}
  \hat{\sigma}_R^2 &= P^{-1} \sum_{t=R+1}^{T-1} (D_{Rt} - \oosA)^2 \\
  &= 4 \hat{\theta}_{2R}^{R\prime} \Big[P^{-1} \sum_{t=R+1}^{T-1}
  \Big(y_{t+1} x_{2t} - P^{-1} \sum_{s=R+1}^{T-1} y_s x_{2s}\Big)
  \Big(y_{t+1} x_{2t} - P^{-1} \sum_{s=R+1}^{T-1} y_s
  x_{2s}\Big)'\Big] \hat{\theta}_{2R}^{R\prime} \\ & \quad - 4
  \Big[P^{-1} \sum_{t=R+1}^{T-1} \Big(y_{t+1} x_{2t} - P^{-1}
  \sum_{s=R+1}^{T-1} y_s x_{2s}\Big)' \hat{\theta}_{2R}^{R}
  \hat{\theta}_{2R}^{R\prime} \Big(x_{2t} x_{2t}' - P^{-1}
  \sum_{s=R+1}^{T-1} x_{2s} x_{2s}' \Big) \hat{\theta}_{2R}^{R} \Big]
  \\ &\quad + P^{-1} \sum_{t=R+1}^{T-1}
  \Big[\hat{\theta}_{2R}^{R\prime} \Big(x_{2t} x_{2t}' - P^{-1}
  \sum_{s=R+1}^{T-1} x_{2s} x_{2s}' \Big) \hat{\theta}_{2R}^{R}  \Big]^{2}.
\end{align*}
As $P \to \infty$, the first term converges in probability to
$\hat{\theta}_{2R}^{R\prime} \hat{\theta}_{2R}^R$, the second to zero,
and the third to $\E_R(\hat{\theta}_{2R}^{R\prime}(I - x_{2t}x_{2t}')
\hat{\theta}_{2R}^R)^2$.  Since the number of regressors prevents
$\hat{\theta}_{2R}^R$ from converging i.p. to zero (its expected
value), $\hat{\sigma}_R^2$ does not converge to the unconditional
variance.

@@

Finally, we can look at the difference $\E_R \bar{D}_R - \E_T
\bar{D}_T$.  We can write this as
\begin{align*}
  \E_R \oosA - \E_T \oosB &= \hat{\theta}_{2R}^{R\prime}
  \hat{\theta}_{2R}^R - \hat{\theta}_{2T}^{T\prime}
  \hat{\theta}_{2T}^T \\ &=
  \eb_T'[\tilde{X}_{2R}(X_{2R}'X_{2R})^{-2}
  \tilde{X}_{2R} - X_{2T}(X_{2T}'X_{2T})^{-2} X_{2T} ] \eb_T
\end{align*}
with $\tilde{X}_{2R}$ the $T \times K_2$ matrix $[X_{2R}'\ 0]'$.
Standard results for the moments of quadratic forms and of the
Inverse-Wishart distribution \citep{Haf:79} imply that
\begin{equation*}
  \E(\E_R \oosA - \E_T \oosB) = \frac{K_2 P}{(T - K_2 - 1)(R - K_2 - 1)}
\end{equation*}
and
\begin{align*}
  \var(\E_R & \oosA - \E_T \oosB) \\ &= \E
  \big[\tr((X_{2R}'X_{2R})^{-1} - (X_{2T}'X_{2T})^{-1})\big]^2 + 2 \tr
  \E\big((X_{2R}'X_{2R})^{-2} - (X_{2T}'X_{2T})^{-2}\big) \\ &\quad - \big[\tr
  \E((X_{2R}'X_{2R})^{-1} - (X_{2T}'X_{2T})^{-1}) \big]^2 \\ &=
  O(P/T)^2.
\end{align*}
So, in this example, $P^{1/2}(\E_R \oosA - \E_T \oosB) \to^p 0$ only
if $P^3/T^2 \to 0$, which is slightly weaker than the general
requirement that $P^2/T \to 0$.  If $\lim P^3/T^2 > 0$ the \oos\ average
still obeys the \mds\ \clt, but it is not centered correctly at $\E_T
\oosB$.

@@

\begin{lem}\label{lem-basic-coupling}
  Suppose Assumptions \ref{asmp-1}--\ref{asmp-3} hold.  Then, for any
  T, $s$, $t$, $u$, and $w$, with $t \geq s > u \geq w$, there exist random
  variables $\tilde D_s,\dots,\tilde D_t$ such that
  \begin{equation}\label{eq:coupling1}
    P[(\tilde D_s,\dots,\tilde D_t) \neq (D_{sw},\dots,D_{tw})] \leq \beta_{s-u}
  \end{equation}
  and
  \begin{equation}\label{eq:coupling2}
    \E(\phi(\tilde D_s,\dots, \tilde D_t) \mid \mathcal{F}_u ) = 
    \int
    \phi(D_{sw},\dots,D_{tw}) f(\mathbf{x}, \mathbf{y})\ d\mathbf{x}\ d\mathbf{y}
  \end{equation}
  almost surely for all measurable functions $\phi$ such that the
  expectations are finite, where 
  \[ \mathbf{x} = (x_{s}', \dots, x_{t}')', \qquad
  \mathbf{y} = (y_{s+\h},\dots,y_{t+\h})',\] and $f$ is the
  joint density of $(\mathbf{x}, \mathbf{y})$.  Moreover,
 \begin{equation}\label{eq:coupling3}
   \| \tilde D_v - D_{vw} \|_2 \leq 2^{1+1/\rho} B_L
   \beta_{s-u}^{\rhoExp}, \qquad v = s,\dots,t.
 \end{equation}
\end{lem}

@@

  Now define
  \[ \tilde D_v \equiv L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_w)
  - L(y_{v+\h}^* - x_{2v}^{*\prime} \hat{\theta}_w), \quad v =
  s,\dotsc, t,
  \]
  with $y_{v+\h}^*$ and $x_{iv}^*$ denoting the elements of $V^*$
  corresponding to $y_{v+\h}$ and $x_{iv}$ in $V_s$.  Equations
  (\ref{eq:coupling1}) and (\ref{eq:coupling2}) are satisfied by
  construction, and (\ref{eq:coupling3}) follows from Lemma
  \ref{lem-extend-mp}.
\end{proof}

\begin{lem}\label{lem:a2}
  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-3} and that the fixed
  window scheme is used.  Let $b_T$ be a sequence such that $b_T \to
  \infty$ and $b_T = o(P)$ and define
  \begin{equation*}
    Z_i = \ZDef.
  \end{equation*}
  Then
  \begin{equation}
    \label{eq:10}
    \sum_{i=1}^{\lfloor P/b_T \rfloor} (\E_R Z_i^2 - \E_{R+(i-1) b_T}
    Z_i^2) \to^p 0.
  \end{equation}
  If Assumptions~\ref{asmp-4} and \ref{asmp-5} also hold and we define
  \begin{gather*}
    Z_{1t} = \varianceTermIIIa, \intertext{and} Z_{2t} =
    \varianceTermIVb,
  \end{gather*}
  then
  \begin{equation}
    \label{eq:12}
    \sum_{t=-P+1}^{2P} (Z_{1t} Z_{2t} - \E_R Z_{1t} Z_{2t}) \to^p 0.
  \end{equation}
\end{lem}
\begin{proof}
\newcommand{\UFiltration}[1]{\ensuremath{\mathcal{F}_{(#1)b_{T}+R-P}}}%
The first result,~\eqref{eq:10}, follows a similar argument to Lemma~5
of \citet{Jon:97} and~\eqref{eq:12} to Lemma~A.4 of \citet{JoD:00}.
Since these arguments are similar and our modification is the same for
both, we'll just present the more complicated version,~\eqref{eq:12}.

>>>>

Both models are estimated using \ols\ with a fixed window:
\[
\hat y_{i,t+\h} = x_{it}'\hat{\theta}_{it}, \qquad i=1,2, \qquad t
= R+1,\dots,T-h
\]
with
\begin{equation*}
  \bh{it} =
  \begin{cases}
    \big(\sum_{s=1}^{R-\h} x_{is}x_{is}'\big)^{-1} \sum_{s=1}^{R-\h}
    x_{is} y_{s+\h} & t \leq T \\
    \big(\sum_{s=1}^{T-\h} x_{is}x_{is}'\big)^{-1}
    \sum_{s=1}^{T-\h} x_{is} y_{s+\h} & t > T.
  \end{cases}
\end{equation*}
The observed \oos\ average is denoted $\oosA$: \[\oosA \equiv P^{-1}
\oosSum{t}{1} D_{Rt}\]  with
\[
D_{Rt} \equiv L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}).
\]
The \oos\ statistic of interest is $\oost \equiv \sqrt{P} \oosA /
\hat\sigma_R$, for $\hat\sigma_R^2$ some (possibly Heteroskedasticity- and
Autocorrelation-Consistent, or \hac) estimator of the asymptotic
variance of $\oosA$.

As discussed above, the forecaster's goal is to choose the model with
lower average future loss; i.e. to determine whether $\oosB$ is
positive or negative,with
\[
\oosB \equiv Q^{-1} \sum_{t=T+1}^{T+Q} D_{Tt}, \quad 
D_{Tt} \equiv L(y_{t+h} - x_{1t}' \bh{1t}) - L(y_{t+h} - x_{2t}' \bh{2t}).
\]
Note that the coefficients are reestimated with the full dataset.
Since the forecaster's information set, $\mathcal{F}_T$, does not
contain $\oosB$, he or she should decide between the models based on
the conditional expectation, $\E_T \oosB$. If this quantity is
positive, the first model is expected to perform the worst in the
future, and if it is negative the second is.

@@

\begin{asmp} \label{asmp-4} $P, R, Q \to\infty$ and $P^2/T \to 0$ as
  $T \to \infty$.
\end{asmp}

@@

Assumptions~\ref{asmp-1}--\ref{asmp-5} are broadly similar to
\citepos{Wes:96} assumptions, except with regard to model complexity
and the size of the test sample.  West assumes that $K_1$ and $K_2$
are both finite, while we let them grow rapidly with $T$
(Assumption~\ref{asmp-1}), and West lets $P/R$ converge to any value
in $[0,\infty]$, while we require $P^2/R \to 0$
(Assumption~\ref{asmp-4}).\footnote{\citet{Wes:96} does not have a
  second \oos\ period, so there is no analogue in his paper to our
  restriction on $Q$.}  Obviously, these differences are
related---allowing for complex models requires tighter constraints on
the size of the test sample.  West allows more general estimation
methods, while we restrict attention to \ols; the advantage of using
\ols\ is that we can derive the inequality, 
\begin{equation*}
  \| x_{it}'\theta_{i,T+1} - x_{it}'\theta_{iR} \|_2 \leq O(P/T)^{1/2}.
\end{equation*}
Our main results will hold for other models and estimation windows as
long as a similar inequality exists, but proving such inequalities is
left for future research.

@@

Two intermediate Lemmas will help us understand Theorem
\ref{res-confidence-intervals} better.  Its proof consists of two
steps: we can write
\begin{equation}
  \sqrt{P} (\oosA - \E_T \oosB) = \sqrt{P} (\oosA - \E_R
  \oosA) + \sqrt{P} (\E_R \oosA - \E_T \oosB),
\end{equation}
so Theorem~\ref{res-confidence-intervals} holds if
\begin{equation}\label{coefpart}
  \E_R \oosA = \E_T \oosB + o_p(P^{-1/2}).
\end{equation}
and
\begin{equation}\label{normalpart}
  \sqrt{P}\frac{\oosA - \E_R \oosA}{\sigma_R} \to^d N(0,1)
\end{equation}
The first Lemma establishes~\eqref{coefpart} and the second shows that
the process $\{D_{Rt} - \E_R \oosA\}$ is an $L_2$-mixingale of size
$-1/2$ that satisfies a \clt, ensuring~\eqref{normalpart}.

\begin{lem} \label{res-convergence}
  Under Assumptions \ref{asmp-1}--\ref{asmp-4},
  \begin{equation}\label{eq:7}
    \E_T \oosB - \E_R \oosA = O_p(\sqrt{P/T}) + o_p(P^{-1/2} + Q^{-1/2}).
  \end{equation}
\end{lem}

Note that $\E_T \oosB - \E_R \oosA$ is noise introduced by
approximating the performance of the full-sample estimates with that
of the partial-sample estimates.  Moreover, the $O_p(\sqrt{P/T})$ term
is binding; it is straightforward to find examples for which
$\sqrt{T/P}(\E_T \oosB - \E_R \oosA)$ does not converge to
zero.\footnote{Notice that, if the observations are i.i.d. and
  $(y_{t+h}, x_{it}) \sim N(0,I)$, $(\hat{\theta}_{iR}^R -
  \hat{\theta}_{iT}^T) \sim N(0, (X_{iR}'X_{iR})^{-1} -
  (X_{iT}'X_{iT})^{-1})$ given $X_{iT}$, and so
  $\var(x_{i,T+1}'\hat{\theta}_{iR}^R - x_{i,T+1}'
  \hat{\theta}_{iT}^T) \gg P K_i / (R - K_2)(T - K_2)$.}
Consequently, there is little scope to relax our assumption that
$P^2/T \to 0$.  If $\lim P^2/T$ is positive and finite then there is
the possibility of adjusting the asymptotic distribution of the test
statistic to account for this noise term as in \citet{Wes:96}, but we
leave that to future research.  If $P^2/T \to \infty$, which is
closest to common practice in applied research, the noise term
dominates the asymptotic distribution of the \oos\ $t$-test and the
test has only trivial power in the limit if it has correct size.

@@

  \noindent Part 2: Moreover,~\eqref{normalpart} holds under
  Assumptions~\ref{asmp-1}--\ref{asmp-4} if $\sigma_R^2$ is
  a.s. uniformly positive.
\end{lem}

@@

\begin{lem}
  \label{res-variance-estimator} Suppose Assumptions
  \ref{asmp-1}--\ref{asmp-5} hold and that $\gamma \to \infty$ and 
  $\gamma/P \to 0$ as $T \to \infty$, and define
  \begin{equation*}
    \hat{\sigma}_R^2 \equiv P^{-1} \oosSum{s,t}{1} (D_{Rt} - \oosA)(D_{Rs} - \oosA)
    \vWeight.
  \end{equation*}
  Then $\hat{\sigma}_R^2 - \sigma_R^2 \to^p 0$.
\end{lem}

@@

Let $L(e) = e^2$, let $h
= 1$, let the benchmark model have no regressors (i.e. $y_{t+1} \sim$
white noise), suppose that $(y_{t}, x_{2t}) \sim i.i.d.\ N(0,I)$, and
assume that $R > 2K_2 + 4$.\footnote{The restriction $R > 2 K_2 + 4$
  allows us to use a convenient formula for moments of the
  Inverse-Wishart distribution.}  Under these conditions,
\begin{equation*}
  D_t =
  \begin{cases}
    2 y_{t+1} x_{2t}'\hat{\theta}_{2R} -
    \hat{\theta}_{2R}' x_{2t} x_{2t}' \hat{\theta}_{2R} & t \leq T \\
    2 y_{t+1} x_{2t}'\hat{\theta}_{2T} -
    \hat{\theta}_{2T}' x_{2t} x_{2t}' \hat{\theta}_{2T} & t > T.
  \end{cases}
\end{equation*}

The first two conditional moments of $D_t$ for $t > R$ (given
$\mathcal{F}_R$) are straightforward to derive: $\E_R D_{Rt} = -
\hat{\theta}_{2R}' \hat{\theta}_{2R}$ and
\begin{equation*}
  \sigma_R^2 \equiv \E_R(D_{Rt} - \E_R D_{Rt})^2 = 4
  \hat{\theta}_{2R}^{R\prime} \hat{\theta}_{2R}^{R} +
  \E_R(\hat{\theta}_{2R}^{R\prime} (I - x_{2t} x_{2t}')
  \hat{\theta}_{2R}^{R})^2   \geq 4 \hat{\theta}_{2R}^{R\prime}
  \hat{\theta}_{2R}^R \quad a.s.
\end{equation*}
Now, $\hat{\theta}_{2R}' \hat{\theta}_{2R}$ is
a.s. positive and uniformly integrable with mean $4 K_2 / (R - K_2 -
1)$ (since $(X_{2R}'X_{2R})^{-1}$ is Inverse-Wishart$(I_{K_2}, R)$),
making $\sigma_R^2$ uniformly a.s. positive and ensuring that the
distribution of the \oos\ average is not $P^{1/2}$-degenerate.  The
natural \oos\ variance estimator is consistent for $\sigma_R^2$:
\begin{align*}
  \hat{\sigma}_R^2 &= P^{-1} \sum_{t=R+1}^{T-1} (D_{Rt} - \oosA)^2 \\
  &= 4 \hat{\theta}_{2R}^{R\prime} \Big[P^{-1} \sum_{t=R+1}^{T-1}
  \Big(y_{t+1} x_{2t} - P^{-1} \sum_{s=R+1}^{T-1} y_s x_{2s}\Big)
  \Big(y_{t+1} x_{2t} - P^{-1} \sum_{s=R+1}^{T-1} y_s
  x_{2s}\Big)'\Big] \hat{\theta}_{2R}' \\ & \quad - 4
  \Big[P^{-1} \sum_{t=R+1}^{T-1} \Big(y_{t+1} x_{2t} - P^{-1}
  \sum_{s=R+1}^{T-1} y_s x_{2s}\Big)' \hat{\theta}_{2R}
  \hat{\theta}_{2R}' \Big(x_{2t} x_{2t}' - P^{-1}
  \sum_{s=R+1}^{T-1} x_{2s} x_{2s}' \Big) \hat{\theta}_{2R} \Big]
  \\ &\quad + P^{-1} \sum_{t=R+1}^{T-1}
  \Big[\hat{\theta}_{2R}' \Big(x_{2t} x_{2t}' - P^{-1}
  \sum_{s=R+1}^{T-1} x_{2s} x_{2s}' \Big) \hat{\theta}_{2R}'  \Big]^{2}.
\end{align*}
As $P \to \infty$, the first term converges in probability to
$\hat{\theta}_{2R}^{R\prime} \hat{\theta}_{2R}^R$, the second to zero,
and the third to $\E_R(\hat{\theta}_{2R}^{R\prime}(I - x_{2t}x_{2t}')
\hat{\theta}_{2R}^R)^2$.  Since the number of regressors prevents
$\hat{\theta}_{2R}^R$ from converging i.p. to zero (its expected
value), $\hat{\sigma}_R^2$ does not converge to the unconditional
variance.

@@

Finally, we can look at the difference $\E_R \bar{D}_R - \E_T
\bar{D}_T$.  We can write this as
\begin{align*}
  \E_R \oosA - \E_T \oosB &= \hat{\theta}_{2R}'
  \hat{\theta}_{2R} - \hat{\theta}_{2T}' \hat{\theta}_{2T} \\ &=
  \eb_T'[\tilde{X}_{2R}(X_{2R}'X_{2R})^{-2}
  \tilde{X}_{2R} - X_{2T}(X_{2T}'X_{2T})^{-2} X_{2T} ] \eb_T
\end{align*}
with $\tilde{X}_{2R}$ the $T \times K_2$ matrix $[X_{2R}'\ 0]'$.
Standard results for the moments of quadratic forms and of the
Inverse-Wishart distribution \citep{Haf:79} imply that
\begin{equation*}
  \E(\E_R \oosA - \E_T \oosB) = \frac{K_2 P}{(T - K_2 - 1)(R - K_2 - 1)}
\end{equation*}
and
\begin{align*}
  \var(\E_R & \oosA - \E_T \oosB) \\ &= \E
  \big[\tr((X_{2R}'X_{2R})^{-1} - (X_{2T}'X_{2T})^{-1})\big]^2 + 2 \tr
  \E\big((X_{2R}'X_{2R})^{-2} - (X_{2T}'X_{2T})^{-2}\big) \\ &\quad - \big[\tr
  \E((X_{2R}'X_{2R})^{-1} - (X_{2T}'X_{2T})^{-1}) \big]^2 \\ &=
  O(P/T)^2.
\end{align*}
So, in this example, $P^{1/2}(\E_R \oosA - \E_T \oosB) \to^p 0$ only
if $P^3/T^2 \to 0$, which is slightly weaker than the general
requirement that $P^2/T \to 0$.  If $\lim P^3/T^2 > 0$ the \oos\ average
still obeys the \mds\ \clt, but it is not centered correctly at $\E_T
\oosB$.

@@

\begin{lem}\label{lem-basic-coupling}
  Suppose Assumptions \ref{asmp-1}--\ref{asmp-3} hold.  Then, for any
  T, $s$, and $t$ with $t \geq s$, there exist random variables
  $\tilde D_s,\dots,\tilde D_t$ such that
  \begin{equation}\label{eq:coupling1}
    P[(\tilde D_s,\dots,\tilde D_t) \neq (D_s,\dots,D_t)] \leq \beta_{s-u}
  \end{equation}
  and
  \begin{equation}\label{eq:coupling2}
    \E(\phi(\tilde D_s,\dots, \tilde D_t) \mid \mathcal{F}_u ) = 
    \int
    \phi(D_s,\dots,D_t) f(\mathbf{x}, \mathbf{y})\ d\mathbf{x}\ d\mathbf{y}
  \end{equation}
  almost surely for all measurable functions $\phi$ such that the
  expectations are finite, where 
  \[ \mathbf{x} = (x_{s}', \dots, x_{t}')', \qquad
  \mathbf{y} = (y_{s+\h},\dots,y_{t+\h})',\] and $f$ is the
  joint density of $(\mathbf{x}, \mathbf{y})$.  Moreover,
 \begin{equation}\label{eq:coupling3}
   \| \tilde D_v - D_v \|_2 \leq 2^{1+1/\rho} B_L
   \beta_{s-u}^{\rhoExp}, \qquad v = s,\dots,t.
 \end{equation}
\end{lem}

@@

  Now define
  \begin{equation*}
    \tilde D_v =
    \begin{cases}
      L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_{1R}) - L(y_{v+\h}^* -
      x_{2v}^{*\prime} \hat{\theta}_{2R}) & v \leq T \\
      L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_{1T}) - L(y_{v+\h}^* -
      x_{2v}^{*\prime} \hat{\theta}_{2T}) & v > T
    \end{cases}
  \end{equation*}
  with $y_{v+\h}^*$ and $x_{iv}^*$ denoting the elements of $V^*$
  corresponding to $y_{v+\h}$ and $x_{iv}$ in $V_s$.  Equations
  (\ref{eq:coupling1}) and (\ref{eq:coupling2}) are satisfied by
  construction, and (\ref{eq:coupling3}) follows from Lemma
  \ref{lem-extend-mp}.
\end{proof}

\begin{lem}\label{lem:a2}
  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-3} hold.  Let $b_T$ be a
  sequence such that $b_T \to \infty$ and $b_T = o(P)$ and define
  \begin{equation*}
    Z_i = \ZDef.
  \end{equation*}
  Then
  \begin{equation}
    \label{eq:10}
    \sum_{i=1}^{\lfloor P/b_T \rfloor} (\E_R Z_i^2 - \E_{R+(i-1) b_T}
    Z_i^2) \to^p 0.
  \end{equation}
  If Assumptions~\ref{asmp-4} and \ref{asmp-5} also hold and we define
  \begin{gather*}
    Z_{1t} = \varianceTermIIIa, \intertext{and} Z_{2t} =
    \varianceTermIVb,
  \end{gather*}
  then
  \begin{equation}
    \label{eq:12}
    \sum_{t=-P+1}^{2P} (Z_{1t} Z_{2t} - \E_R Z_{1t} Z_{2t}) \to^p 0.
  \end{equation}
\end{lem}
\begin{proof}
\newcommand{\UFiltration}[1]{\ensuremath{\mathcal{F}_{(#1)b_{T}+R-P}}}%
The first result,~\eqref{eq:10}, follows a similar argument to Lemma~5
of \citet{Jon:97} and~\eqref{eq:12} to Lemma~A.4 of \citet{JoD:00}.
Since these arguments are similar and our modification is the same for
both, we'll just present the more complicated version,~\eqref{eq:12}.
